Tidy Amicus Data

### 2021-11-04 data-cleaning/00-scrape-amicus-text.Rmd
amicus structure
scrape text w/shorten keyword

```{r}
# number of cores available
n_cores <- detectCores() - 1

@@

Check what we have - count of amicus briefs by case for manual comparision

@@

@@

```{r}
box_write(amicus_txt,
          file_name = "raw-amicus-brief-text.csv",
          dir_id = '145990409196')
```

>>>>

```{r}
# number of cores available
n_cores <- detectCores() - 1
registerDoParallel(n_cores)

@@

Check what we have - count of amicus briefs by case for manual comparison

@@

Save list of amicus file IDs on Box

```{r}
amicus_file_ids %>% 
  right_join(., case_folders, "case") %>% 
  select(-id.y) %>% 
  rename(id = id.x) %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
  box_write(., "amicus-file-ids.csv", dir_id = "145990409196")
```

@@

```{r}
box_write(amicus_txt,
          file_name = "shortened-amicus-brief-text.csv",
          dir_id = '145990409196')
```
